Relationship between solar wind, $D_{st}$, and plasmasphere mass density on one-hour time scales

### 2015-09-03 paper.tex

\subsection{D$_{st}$ and $\rho_{eq}$ Events}

@@

In the upper panel of \label{DailyAverages}, $D_{st}$ events are shown.  The minimum $D_{st}$ median is $-48$~nT.  Consistent with \cite{Takahashi2010}, $D_{st}$ events correspond to elevated $\rho_{eq}$, although the magnitude of increase observed here is $\sim2$ amu/cm$^3$ instead of the value of ~10 amu/cm$^3$ found in \cite{Takahashi2010}.  The vertical green bars in the $\rho_{eq}$ plot show the number of $\rho_{eq}$ values that were used to compute its median and error bars.  Note that for $D_{st}$, the number of measurements used in computing the medians is much larger as we use all available $D_{st}$ measurements instead of restricting to only values where a non--fill $\rho_{eq}$ value existed.

In the lower panel of \label{DailyAverages}, $\rho_{eq}$ events are shown.  Here we see that $\rho_{eq}$ enhancements do not clearly correspond to a signature in $D_{st}$, but that there is a trend for such enhancments to occur when $B_{z}$ in the IMF is positive.  This is consistent with \cite{Takahashi2010} who note that very large increases in $\rho_{eq}$ often corresponded to movement of the plasmasphere to beyond geosynchronous distances.

@@

This figure shows a definite spike in the $Z$ component of the magnetic field, as well as the defined drop in $DST$, but no obvious change in mass density at an hourly timescale. This points to an issue with only looking at long-timescale trends between density and $D_{st}$, and allows for the possibility that other factors are influencing the long term correlation since there's no obvious connection on a short timescale. One possibility is that, as suggested in \cite{Takahashi2010}, $F_{10.7}$ plays a significant role in driving long term density values which biases the long term correlation of density and $D_{st}$.

@@

\section{More specific events}
It's hypothesized that progressively picking more specific event criteria will allow for the possibility of more significant results, at the expense of more bias in the selection process and potentially less overall usefulness of the results. That said, the predictability of extreme events is of definite interest, so an attempt has been made to find some reproducible method of prediction. Looking at events that last longer than 12 hours and events with an onset threshhold greater than $70g/cm^3$ results in the left and right sides of Figure \ref{Mspec} respectively.

>>>>

\subsection{$D_{st}$ and $\rho_{eq}$ Events}

@@

In the upper panel of \ref{DailyAverages}, $D_{st}$ events are shown.  The minimum $D_{st}$ median is $-48$~nT.  Consistent with \cite{Takahashi2010}, $D_{st}$ events correspond to elevated $\rho_{eq}$, although the magnitude of increase observed here is $\sim 2$ amu/cm$^3$ instead of the value of $\sim 10$ amu/cm$^3$ found in \cite{Takahashi2010}.  The vertical green bars in the $\rho_{eq}$ plot show the number of $\rho_{eq}$ values that were used to compute its median and error bars.  Note that for $D_{st}$, the number of measurements used in computing the medians is much larger as we use all available $D_{st}$ measurements instead of restricting to only values where a non--fill $\rho_{eq}$ value existed.

In the lower panel of \ref{DailyAverages}, $\rho_{eq}$ events are shown.  Here we see that $\rho_{eq}$ enhancements do not clearly correspond to a signature in $D_{st}$, but that there is a trend for such enhancments to occur when $B_{z}$ in the IMF is positive.  This is consistent with \cite{Takahashi2010} who note that very large increases in $\rho_{eq}$ often corresponded to movement of the plasmasphere to beyond geosynchronous distances.

@@

@@

\section{More specific events}
It's hypothesized that progressively picking more specific event criteria will allow for the possibility of more significant results, at the expense of more bias in the selection process and potentially less overall usefulness of the results. That said, the predictability of extreme events is of definite interest, so an attempt has been made to find some reproducible method of prediction. Looking at events that last longer than 12 hours and events with an onset threshhold greater than $70$g/cm$^3$ results in the left and right sides of Figure \ref{Mspec} respectively.
